### 2017-02-07 CO750-ApproximationAlgorithmsTopics/assignments/assignment_01.tex
working on a1

%Q5
\section{}
\paragraph{}
Let $G=(V,E)$ be a metric graph with edge lengths $d: E \rightarrow \N_+$ and let $f : 2^V \rightarrow \N_+$  be a a function satisfying:
\begin{enumerate}
\item (Symmetric) $f(S) = f(V\backslash S)$ for all $S \subseteq V$
\item (Subadditive) $f(A \cup B) = f(A) + f(B)$ for all $A,B \subseteq V$.
\end{enumerate}
Consider the following integer program, to be labelled $IP$:
\begin{align*}
\text{min} \sum_{e \in E} d(e) x_e\\
\text{s.t.} \sum_{e\in \delta(S)} x_e &\geq f(S) &\forall S \subseteq V \\
x &\geq 0, \text{ integer}.
\end{align*}
\paragraph{Solving $IP$ of Trees}
We first observe that this $IP$ is easy to solve on trees. Indeed let $T$ be a tree, and for every $e \in E(T)$ let $S^e$ denote the set of vertices in one of the two connected components of $T-e$. By definition, $\delta(S^e) = \{e\}$. We define the following algorithm $\cA$ to solve $IP$ on a tree $T$:
\begin{enumerate}
\item For all $e \in E(T)$ set $x_e = f(S^e)$.
\item Return $x$.
\end{enumerate}
To see that $\cA$ solves $IP$ on trees, we will show that $(1)$ the solution returned is feasible, and $(2)$ that every feasible $x$ has necessarily $x_e \geq f(S^e)$, implying that the $x$ returned by $\cA$ is optimal.  Let $x$ be the solution returned by $\cA$. To see $(1)$, it is immediate from the definition of $f$ that $x \geq 0$. It remains to verify the cut inequalities. Let $S \subseteq V$. Enumerate $\delta(S)$ as $\delta(S) = \{e_1, \dots, e_k \}$.
\end{document}

>>>>

%Q5
\section{}
\paragraph{}
Let $G=(V,E)$ be a metric graph with edge lengths $d: E \rightarrow \N_+$ and let $f : 2^V \rightarrow \N_+$  be a a function satisfying:
\begin{enumerate}
\item (Symmetric) $f(S) = f(V\backslash S)$ for all $S \subseteq V$
\item (Subadditive) $f(A \cup B) = f(A) + f(B)$ for all $A,B \subseteq V$.
\end{enumerate}
Consider the following integer program, to be labelled $IP$:
\begin{align*}
\text{min} \sum_{e \in E} d(e) x_e\\
\text{s.t.} \sum_{e\in \delta(S)} x_e &\geq f(S) &\forall S \subseteq V \\
x &\geq 0, \text{ integer}.
\end{align*}
\paragraph{Solving $IP$ of Trees}
We first observe that this $IP$ is easy to solve on trees. Indeed let $T$ be a tree, and for every $e \in E(T)$ let $S^e$ denote the set of vertices in one of the two connected components of $T-e$. By definition, $\delta(S^e) = \{e\}$. We define the following algorithm $\cA$ to solve $IP$ on a tree $T$:
\begin{enumerate}
\item For all $e \in E(T)$ set $x_e = f(S^e)$.
\item Return $x$.
\end{enumerate}
To see that $\cA$ solves $IP$ on trees, we will show that $(1)$ the solution returned is feasible, and $(2)$ that every feasible $x$ has necessarily $x_e \geq f(S^e)$, implying that the $x$ returned by $\cA$ is optimal.  Let $x$ be the solution returned by $\cA$. 
\paragraph{}
To see $(1)$, it is immediate from the definition of $f$ that $x \geq 0$. It remains to verify the cut inequalities. Let $S \subseteq V$. Enumerate $\delta(S)$ as $\delta(S) = \{e_1, \dots, e_k \}$. For each $i = 1, \dots, k$ define
$$S_i = \{ v \in S : v \text{ can reach an endpoint of } e_i \text{ via a path internal to } S\}.$$
Since $T$ is connected, each node $v \in S$ can reach each node in $V \backslash S$, and must use an edge $e_i \in \delta(S)$ to do so. The vertex $v$ is assigned to $S_i$ where $e_i$ is the first edge in $\delta(S)$ on any such path across the cut. Hence $S = \cup_i S_i.$ Further $S_i \subseteq S^{e_i}$ or $S_i \subseteq V\backslash S^{e_i}$. To see this, observe that if it were to fail then there would exist $u, v \in S_i$ with $u \in S^{e_i}$ and $v \in V\backslash S^{e_i}$. But then $u$ and $v$ are connected internally within $S$ (since they both can internally reach an endpoint of $e_i$) and so removing $e_i$ does not separate them, violating that $u \in S^{e_i}$ and $v \in V\backslash S^{e_i}$. Thus
\end{document}
